Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-10 acknowledgments.tex
added CU/Boulder.

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Tech,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University,
 the San Diego Supercomputer Center (through the Strategic Applications
Partner program and the Director’s office),
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Stanford University,
the University of Arizona,
the University of Califoria at San Diego, 
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.

>>>>

We acknowledge the  many academic institutions that have supported \enzo\
development, including (in alphabetical order)
Columbia University,
Georgia Tech,
Michigan State University and the MSU Institute for Cyber-Enabled
Research, 
the National Center for Supercomputing Applications, 
the Pennsylvania State University,
 the San Diego Supercomputer Center (through the Strategic Applications
Partner program and the Director’s office),
SLAC National Accelerator Laboratory,
the SLAC/Stanford Kavli Institute for Particle
Astrophysics and Cosmology,  
Stanford University,
the University of Arizona,
the University of Califoria at San Diego, 
the University of Colorado at Boulder,
the University of Florida,
and the University of Illinois.
We acknowledge support from the Kavli Institute for Theoretical
Physics at Santa Barbara, the Aspen Center for Physics, and the UCLA
Institute for Pure and Applied Mathematics, which have
generously hosted \enzo\ developers through their conference and
workshop programs.
